---
title: "ProfsOnParadePollAnalysis"
author: "Meghan Duffy"
date: "1/27/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analysis of poll asking Dynamic Ecology readers about their experiences with "Professors on Parade"-style courses
Poll appeared January 24, 2017 and closed on January 26, 2017
Blog post url:
https://dynamicecology.wordpress.com/2017/01/24/poll-have-you-been-involved-in-a-professors-on-parade-course-was-it-useful/

The poll received 100 responses.

###Q1: Were you involved in this course as a student or presenter?
```
1 = student
2 = presenter
```

###Q2: What type of department or program was the course in? (Choose the option that is most similar to the target audience for the course)
```
1 = ecology and evolutionary biology
2 = biology
3 = molecular & cell biology
4 = natural resources
5 = other
```

###Q3: Who were the students in the course?
```
1 = just grad students
2 = just undergrads
3 = both grad students and undergrads
```

###Q4: Who were the presenters in the course?
```
1 = just faculty
2 = faculty and grad students
3 = faculty, grad students, and people outside academia
```

###Q5: What was the course content? (choose all that apply)
```
1 = research presentations
2 = basic science skills (e.g., how to make a poster)
3 = basic research skills (e.g., how to extract DNA)
4 = career advice and prospects
5 = introduction to a general research area (e.g., ecology)
6 = discussion of papers written by department faculty
7 = discussion of classic/important papers in the field
```

###Q6: Do you think the course was useful? (In other words: would most students think it was a good use of their time?)
```
1 = yes
2 = no
```

Note: I did the above coding of the responses by hand in excel. Ideally, I'd check things one more time to make sure I didn't make an error (especially for Q5), but I'm trying not to allow this to take up a ton of time!

## Results
```{r, load libraries, message=FALSE, echo=FALSE}
library(ggplot2)
library(dplyr)
```

```{r, read in data}
polldata <- read.csv("PoPpollresults012617.csv", na.strings = "?")
head(polldata)
str(polldata)
```

```{r, quick look at whether faculty & students like the course differently}
LikedSum <- 
  polldata %>%
  filter(!is.na(useful01)) %>%
  group_by(involved01,useful01) %>%
  summarise(n=n()) %>%
  mutate(rel.freq = round(100 * n/sum(n), 0))

LikedSum
```

```{r, quick look at effect of research presentation component}
LikedSumResearch <- 
  polldata %>%
  filter(!is.na(useful01)) %>%
  group_by(researchpres01,useful01) %>%
  summarise(n=n()) %>%
  mutate(rel.freq = round(100 * n/sum(n), 0))

LikedSumResearch
```

```{r, quick look at effect of presenters}
LikedSumPresenter <- 
  polldata %>%
  filter(!is.na(useful01)) %>%
  group_by(whowerepresenters,useful01) %>%
  summarise(n=n()) %>%
  mutate(rel.freq = round(100 * n/sum(n), 0))

LikedSumPresenter

LikedSumPresenter1 <- subset(LikedSumPresenter, useful01==1)

ggplot(LikedSumPresenter1, aes(x=whowerepresenters, y=rel.freq)) +
  geom_bar(stat='identity') +
  ylab("Percent of respondents who found course useful")
```

```{r, quick look at effect of science skills coverage}
LikedSumSciSkills <- 
  polldata %>%
  filter(!is.na(useful01)) %>%
  group_by(basicsciskills01,useful01) %>%
  summarise(n=n()) %>%
  mutate(rel.freq = round(100 * n/sum(n), 0))

LikedSumSciSkills

```

```{r, quick look at effect of research technique coverage}
LikedSumResSkills <- 
  polldata %>%
  filter(!is.na(useful01)) %>%
  group_by(basicresskills01,useful01) %>%
  summarise(n=n()) %>%
  mutate(rel.freq = round(100 * n/sum(n), 0))

LikedSumResSkills

```

```{r, quick look at effect of career advice component}
LikedSumCareerAdvice <- 
  polldata %>%
  filter(!is.na(useful01)) %>%
  group_by(careeradvice01,useful01) %>%
  summarise(n=n()) %>%
  mutate(rel.freq = round(100 * n/sum(n), 0))

LikedSumCareerAdvice

```

```{r, quick look at effect of discussions of faculty papers}
LikedSumFacPapers <- 
  polldata %>%
  filter(!is.na(useful01)) %>%
  group_by(paperdiscdeptfac01,useful01) %>%
  summarise(n=n()) %>%
  mutate(rel.freq = round(100 * n/sum(n), 0))

LikedSumFacPapers

```

```{r, quick look at effect of discussions of classic/impt papers}
LikedSumClassicPapers <- 
  polldata %>%
  filter(!is.na(useful01)) %>%
  group_by(paperdiscclassics01,useful01) %>%
  summarise(n=n()) %>%
  mutate(rel.freq = round(100 * n/sum(n), 0))

LikedSumClassicPapers

```

```{r, quick look for differences between undergrad and grad student courses}
LikedSumStudents <- 
  polldata %>%
  filter(!is.na(useful01)) %>%
  group_by(students01,useful01) %>%
  summarise(n=n()) %>%
  mutate(rel.freq = round(100 * n/sum(n), 0))

LikedSumStudents

```